---
title: 'Defining Dystopia: Text Analysis'
author: "audra white"
date: "3/11/2021"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

### Set Up, Load Libraries

```{r setup, include=FALSE}

# Set Up
library(devtools)
library(gitcreds)
library(renv)
 library(knitr)
library(markdown)

# Basic Packages
library(tidyverse)
library(ggplot2)
library(dplyr)

# Text Analysis
library(readtext) 
library(quanteda)
library(quanteda.textmodels)
library(quanteda.textstats)
library(quanteda.textplots)

knitr::opts_chunk$set(message = TRUE, include = FALSE)
```

# CODE GROUP: CORPA

    absCorp
    refCorp

## CODE: Corpa: absCorp

    ReadText

rTx_2953 rTX1_3772

```{r ReadText: 2 Abstract CSV , include=FALSE}
# Corpus consisting of 2958 documents and 86 docvars.
# [1] 2958   88

rTx_2953 <- readtext("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/DACSS_FL21/DACSS_602_DefiningDystopia/602_DefDys_RProj/CLEANED-DefDys_Ebsco_Nov11_2953.csv")


# Corpus consisting of 2958 documents and 86 docvars.
# [1] 3772   88

rTX1_3772 <- readtext("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/DACSS_FL21/DACSS_602_DefiningDystopia/602_DefDys_RProj/DefDys_Ebsco_Nov11_3772.csv")
```

    Corpa

absCorp

```{r Corpa: 2 Abstract rTXT , include=FALSE}
# Adding corpus objects together
# Corpa of 6725 journal articles with wide search terms for "Dystopia+ and Utopia+"

corp1 <- corpus(rTX1_3772[1:42])
corp2 <- corpus(rTx_2953[1:42])
absCorp <- corp1 + corp2
```

## CODE: Corpa: refCorp

Curated Reference Document.csv

    ReadText

rtx_DysRef

    Corpa

refCorp

```{r Build Corpa, include=FALSE}
# Import second corpa of curated reference documents 
# [1]  50 257

rtx_DysRef <- readtext("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/DACSS_FL21/DACSS_602_DefiningDystopia/602_Dystopia_Data/DefDys_Zotero/DefDys_Ref_Dec2.csv")

refCorp <- corpus(rtx_DysRef)
```

# CODE GROUP: Docvars Categories

    Document-level variables

Title Abstract.Note Manual.Tags Automatic.Tags Item.Type
Publication.Title Publication.Year abscorp - Library.Catalog

    ref Doc Group

```{r Docvars: refCorp Group, echo=TRUE}
refDoc_title <- docvars(refCorp, field = "Title")
refDoc_absNote <- docvars(refCorp, field = "Abstract.Note")
refDoc_manTags <- docvars(refCorp, field = "Manual.Tags")
refDoc_autoTags <- docvars(refCorp, field = "Automatic.Tags" )
refDoc_itemType <- docvars(refCorp, field = "Item.Type")
refDoc_pubTitle <- docvars(refCorp, field = "Publication.Title")
refDoc_pubYear <- docvars(refCorp, field = "Publication.Year")

```

refDoc_title refDoc_absNote refDoc_manTags refDoc_autoTags
refDoc_itemType refDoc_pubTitle refDoc_pubYear

    absDoc Group

```{r Docvars: asbCorp Group , echo=TRUE}

absDoc_title <- docvars(absCorp, field = "Title")
absDoc_absNote<- docvars(absCorp, field = "Abstract.Note")
absDoc_manTags <- docvars(absCorp, field = "Manual.Tags")
absDoc_autoTags <- docvars(absCorp, field = "Automatic.Tags" )
absDoc_itemType <- docvars(refCorp, field = "Item.Type" )
absDoc_pubTitle <- docvars(absCorp, field = "Publication.Title")
absDoc_pubYear <- docvars(absCorp, field = "Publication.Year")
absDoc_libCat <- docvars(absCorp, field = "Library.Catalog")

```

absDoc_title absDoc_absNote absDoc_manTags absDoc_autoTags
absDoc_itemType absDoc_pubTitle absDoc_pubYear absDoc_libCat

# CODE GROUP: CORPUS SUBSET

## CODE: Corpus Subset: Signal

Document Level Variables: Title Manual.Tags

    Signal - Corpus Subset

```{r Corpus Subset: refCorp: Signal, include=FALSE}

s_tle_refCorpSub <- corpus_subset(refCorp, Title %in% 
  c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )

s_mTag_refCorpSub <- corpus_subset(refCorp, Manual.Tags %in%
   c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )                                  

```

s_tle_refCorpSub s_mTag_refCorpSub

```{r Corpus Subset: absCorp: Signal, include=FALSE}

s_tle_absCorpSub <- corpus_subset(absCorp, Title %in% 
  c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )   

s_mTag__absCorpSub <- corpus_subset(absCorp, Manual.Tags %in%
  c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )   

```

s_title_absCorpSub s_mTag\_\_absCorpSub

## CODE: Corpus Subset: Noise

Document Level Variables: Title Manual.Tags

```{r Corpus Subset: refCorp: Noise;, include=FALSE}

n_tle_refCorpSub <- corpus_subset(refCorp, Title %in% 
   c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)


n_mTag_refCorpSub <- corpus_subset(refCorp, Manual.Tags %in% 
  c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)


```

n_tle_refCorpSub n_MTag_refCorpSub

```{r Corpus Subset: absCorp: Noise;, include=FALSE}

n_tle_absCorpSub <- corpus_subset(absCorp, Title %in% 
  c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)


n_mTag_absCorpSub <- corpus_subset(absCorp, Manual.Tags %in%
  c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)

```

n_tle_absCorpSub n_mTag_absCorpSub

# RETURNS: CORPUS SUBSET: Signal & Noise

    Signal 
      refCorpSub Group

s_tle_refCorpSub returns: 11 s_mTag_refCorpSub returns: 1

    Signal 
      absCorpSub Group

s_tle_absCorpSub returns: 0 s_mTag\_\_absCorpSub returns: 0

    Noise
      refCorpSub Group

n_tle_refCorpSub returns: 14 n_MTag_refCorpSub returns: 1

    Noise
      absCorp Group

n_tle_absCorpSub returns: 7 n_mTag_absCorpSub returns: 0

# CODE GROUP: Tokens

## CODE: Tokens: Corpa

    absTok
    refTok

```{r Tokenize: AbsCorp & RefCorp eval=FALSE, include=FALSE}
# Tokenize 
absTok <- tokens(absCorp, remove_punct = TRUE)
refTok <- tokens(refCorp, remove_punct = TRUE)

```

## CODE: Tokens: Docvars Categories

Docvars Categories Title Abstract.Note Manual.Tags Automatic.Tags
Item.Type Publication.Title Publication.Year //numbers cannot be
tokenized// abscorp - Library.Catalog

      refTok Group 

```{r Tokenize: RefDoc Group, echo=TRUE}

title_refTok <- tokens(refDoc_Title)

absNote_refTok <- tokens(refDoc_AbsNote)

manTag_refTok <- tokens(refDoc_ManTags)

itmTyp_refTok <- tokens(refDoc_itemType)

pubTle_refTok <- tokens(refDoc_pubTitle)

```

title_refTok absNote_refTok manTag_refTok itmTyp_refTok pubTle_refTok

    absTok Group

```{r Tokenize: absDoc Group, echo=TRUE}

title_absTok <- tokens(absDoc_Title)

absNote_absTok <- tokens(absDoc_AbsNote)

manTag_absTok <- tokens(absDoc_manTags)

itmTyp_absTok <- tokens(absDoc_itemType)

cent_absTok <- tokens(absDoc_Cent)
```

title_absTok absNote_absTok manTag_absTok itmTyp_absTok cent_absTok

## CODE: Token KWIC: Signal: Dyo Uto

        Titles
        Abstract Notes
        Manual Tags
      
    Signal refKwt Group

```{r Kwic: Signal: refTok Group}

     #Titles
sUto_tle_refKwt <- 
  kwic(title_refTok, pattern = 
         c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_tle_refKwt <- 
  kwic(title_refTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Abstract Note
sUto_aNote_refKwt <- 
  kwic(absNote_refTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)
  

sDyo_aNote_refKwt <- 
  kwic(absNote_refTok, pattern = 
         c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Manual Tags
sUto_mTags_refKwt <- 
  kwic(manTags_refTok,pattern = 
      c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)   

sDyo_mTags_refKwt <- 
  kwic(manTags_refTok,pattern = 
       c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

```

Signal: Titles sUto_tle_refKwt sDyo_tle_refKwt

Signal: Abstract Note sUto_aNote_refKwt sDyo_aNote_refKwt

Signal: Manual Tags sUto_mTags_refKwt sDyo_mTags_refKwt

    Signal: absKwt Group 

```{r Kwic: Signal: absTok Group}

    # Title
sUto_tle_absKwt <- 
  kwic(title_absTok, pattern = 
       c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_tle_absKwt <- 
  kwic(title_absTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Abstract Note
sUto_aNote_absKwt <- 
  kwic(absNote_absTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_aNote_absKwt <- 
  kwic(absNote_absTok, pattern = 
      c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Manual Tags
sUto_mTags_absKwt <- 
  kwic(manTags_absTok,pattern = 
     c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_mTags_absKwt <- 
  kwic(manTags_absTok,pattern = 
    c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

```

Signal: Titles sUto_tle_absKwt sDyo_tle_absKwt

Signal: Abstract Note sUto_aNote_absKwt sDyo_aNote_absKwt

Signal: Manual Tags sUto_mTags_absKwt sDyo_mTags_absKwt

## CODE: Token KWIC: Signal: Wildcard: Uti\* Dyi\*

Signal Wildcard sUti = Utopi *sDyi = Dystopi*

    refKwt Wildcard Group

```{r Kwic: refTok Group: Signal: Wildcards, include=FALSE}

    # Titles 
sUti_tle_refKwt <- kwic(title_refTok,
          pattern = "utopi*", )

sDyi_tle_refKwt <- kwic(title_refTok,
          pattern = "dystopi*", )

    # Abstract Note
sUti_aNote_refKwt <- kwic(absNote_refTok,
          pattern = "utopi*", )

sDyi_aNote_refKwt <- kwic(absNote_refTok,
          pattern = "dystopi*",)

    # Manual Tags
sUti_mTags_refKwt <- kwic(manTags_refTok,
          pattern = "utopi*", )

sDyi_mTags_refKwt <- kwic(manTags_refTok,
          pattern = "dystopi*", )

```

Signal: Wildcards: Titles sUti_tle_refKwt sDyi_tle_refKwt

Signal: Wildcards: Abstract Note sUti_aNote_refKwt sDyi_aNote_refKwt

Signal: Wildcards: Manual Tags sUti_mTags_refKwt sDyi_mTags_refKwt

      absKwt Wildcard Group

```{r Kwic: Signal: absTok Group: Wildcard, eval=FALSE, include=FALSE}

# Titles 
sUti_tle_absKwt <- kwic(title_absTok,
          pattern = "utopi*", )

sDyi_tle_absKwt <- kwic(title_absTok,
          pattern = "dystopi*", )

    # Abstract Note
sUti_aNote_absKwt <- kwic(absNote_absTok,
          pattern = "utopi*", )

sDyi_aNote_absKwt <- kwic(absNote_absTok,
          pattern = "dystopi*",)

    # Manual Tags
sUti_mTags_absKwt <- kwic(manTags_absTok,
          pattern = "utopi*", )

sDyi_mTags_absKwt <- kwic(manTags_absTok,
          pattern = "dystopi*", )

```

Signal: Wildcards: Titles sUti_tle_absKwt sDyi_tle_absKwt

Signal: Wildcards: Abstract Note sUti_aNote_absKwt sDyi_aNote_absKwt

Signal: Wildcards: Manual Tags sUti_mTags_absKwt sDyi_mTags_absKwt

## CODE: Token KWIC: Noise: A,T, D, S

    Noise: refKwt Group

```{r Kwic: Noise: refTok Group, eval=FALSE, include=FALSE}

          # Titles 
nApo_tle_refKwt <- kwic(title_refTok,
          pattern = c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
          )

nTop_tle_refKwt <- kwic(title_refTok,
          pattern = c("Technology", "Society","Fiction")
          )
 
nSub_tle_refKwt <- kwic(title_refTok,
          pattern = c("Novel", "Literature")
          )


          # Abstract Note
nApo_aNote_refKwt <- kwic(absNote_refTok ,
          pattern = c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
          )

nSub_aNote_refKwt  <- kwic(absNote_refTok ,
          pattern = c("Novel", "Literature")
          ) 
            

 nTop_aNote_refKwt <- kwic(absNote_refTok ,
          pattern = c("Technology", "Society","Fiction")
          )

          #Manual Tags
 nApo_mTag_refKwt <- kwic(manTags_refTok ,
          pattern = c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
          )

 nSub_mTag_refKwt  <- kwic(manTags_refTok ,
          pattern = c("Novel", "Literature")
          ) 
            

nTop_mTag_refKwt <- kwic(manTags_refTok ,
          pattern = c("Technology", "Society","Fiction")
          )

```

Noise: Titles nApo_tle_refKwt nTop_tle_refKwt nSub_tle_refKwt

Noise: Abstract Note nApo_aNote_refKwt nSub_aNote_refKwt
nTop_aNote_refKwt

Noise: Manual Tags nApo_mTag_refKwt nSub_mTag_refKwt nTop_mTag_refKwt

    Noise: absKwt Group  

```{r Kwic: Noise: absTok Group, eval=FALSE, include=FALSE}

# Titles 
nApo_tle_absKwt  <- 
  kwic( title_absTok, pattern = 
          c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
        )

nSub_tle_absKwt  <-
  kwic( title_absTok, pattern = 
          c("Novel", "Literature")
        ) 
            

nTop_tle_absKwt <- 
  kwic( title_absTok, pattern = 
          c("Technology", "Society","Fiction")
        )

# Abstract Note
nApo_aNote_absKwt <- 
  kwic( absNote_absTok, pattern = 
          c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
        )

nSub_aNote_absKwt  <- 
  kwic( absNote_absTok, pattern = 
          c("Novel", "Literature")
        ) 
            
nTopaNote_absKwt <- 
  kwic(absNote_absTok,
       pattern = 
         c("Technology", "Society","Fiction")
       )

#Manual Tags
nApo_mTag_refKwt <- 
  kwic( manTag_absTok, pattern = 
          c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
        )

nSub_mTag_refKwt  <- 
  kwic( manTag_absTok, pattern = 
          c("Novel", "Literature")
        ) 
            

nTop_mTag_refKwt <- 
  kwic( manTag_absTok, pattern = 
          c("Technology", "Society","Fiction")
        )

```

Noise: Titles nApo_tle_absKwt nTop_tle_absKwt nSub_tle_refKwt

Noise: Abstract Note nApo_aNote_absKwt nSub_aNote_absKwt
nTop_aNote_refKwt

Noise: Manual Tags nApo_mTag_absKwt nSub_mTag_absKwt nTop_mTag_absKwt

# VISUAL: WordCloud

    TextPlot: Word Cloud Title : Signal & Noise

```{r CODE:   Wordcloud: Dys Wild Card Title, echo=FALSE}
 
tleRefCorp 

# Tokenize & DTM
  
  tle_Dtm <- tleRefCorp %>%
    tokens(remove_punct = T, remove_numbers = T, remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en')) %>%                                     
    tokens_wordstem %>%
    dfm

# Generate Word Cloud
  
textplot_wordcloud(tle_Dtm, max_words = 10)
textplot_wordcloud(tle_Dtm, max_words = 25)
textplot_wordcloud(tle_Dtm, max_words = 50)

```

# 

# 

# CODE GROUP: Works But Not Well

## Chunks: DTM (Document Term Matrix)

Currently not very usefull

    Wordclouds & Freq:
    No features left after trimming with min_count = 3

### CODE: DTM: Corpa

    refDtm
    absDtm

```{r DTM: refTok absTok, include=FALSE}

refDtm <- dfm(refTok)
refDtm


absDtm <- dfm(absTok)
absDtm

summary(absDtm)

```

### CODE: DTM: Corpa Subset

      nTleDtm
      

```{r TEST: DTM: Preprocess, Filter; }
n_tleTok <- n_tle_refCorpSub %>%
  tokens(remove_punct = T, remove_numbers = T, remove_symbols = T) %>%   ## tokenize, removing unnecessary noise
  tokens_tolower %>%                                                     ## normalize
  tokens_remove(stopwords('en')) %>%                                     ## remove stopwords (English)
  tokens_wordstem                                                        ## stemming
n_tleTok

nTleDtm <- dfm(n_tleTok)
nTleDtm

summary(nTleDtm)

```

    accepts:

refCorpSub n_tle_refCorpSub
