---
title: 'Defining Dystopia: Text Analysis'
author: "audra white"
date: "3/11/2021"
output:
  pdf_document: default
  html_document: default
---
### Set Up, Load Libraries
```{r setup, include=FALSE}

# Set Up
library(devtools)
library(gitcreds)
library(renv)
 library(knitr)
library(markdown)

# Basic Packages
library(tidyverse)
library(ggplot2)
library(dplyr)

# Text Analysis
library(readtext) 
library(quanteda)
library(quanteda.textmodels)
library(quanteda.textstats)
library(quanteda.textplots)

# Topic Modeling
library(stm)

knitr::opts_chunk$set(message = TRUE, include = FALSE)
```



#   CODE GROUP: CORPA

    absCorp (2011 - 2021)
    refCorp (1900 - 2021)

###    CODE: Corpa: absCorp
    
    ReadText
rTx_2953
rTX1_3772

```{r ReadText: 2 Abstract CSV , include=FALSE}
# Corpus consisting of 2958 documents and 86 docvars.
# [1] 2958   88

rTx_2953 <- readtext("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/DACSS_FL21/DACSS_602_DefiningDystopia/602_DefDys_RProj/CLEANED-DefDys_Ebsco_Nov11_2953.csv")


# Corpus consisting of 2958 documents and 86 docvars.
# [1] 3772   88

rTX1_3772 <- readtext("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/DACSS_FL21/DACSS_602_DefiningDystopia/602_DefDys_RProj/DefDys_Ebsco_Nov11_3772.csv")
```

    Corpa
absCorp

```{r Corpa: 2 Abstract rTXT , include=FALSE}
# Adding corpus objects together
# Corpa of 6725 journal articles with wide search terms for "Dystopia+ and Utopia+"

corp1 <- corpus(rTX1_3772[1:42])
corp2 <- corpus(rTx_2953[1:42])
absCorp <- corp1 + corp2
```

###    CODE: Corpa: refCorp
Curated Reference Document.csv
    
    ReadText
rtx_DysRef
    
    Corpa
refCorp    
```{r Build Corpa, include=FALSE}
# Import second corpa of curated reference documents 
# [1]  50 257

rtx_DysRef <- readtext("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/DACSS_FL21/DACSS_602_DefiningDystopia/602_Dystopia_Data/DefDys_Zotero/DefDys_Ref_Dec2.csv")

refCorp <- corpus(rtx_DysRef)
```


#   CODE GROUP: Docvars Categories
  
    Document-level variables
  Title
  Abstract.Note
  Manual.Tags
  Automatic.Tags
  Item.Type
  Publication.Title
  Publication.Year 
  abscorp - Library.Catalog
  
###   CODE: Docvar: refDoc Group
```{r Docvars: refCorp Group, echo=TRUE}
refDoc_title <- docvars(refCorp, field = "Title")
refDoc_absNote <- docvars(refCorp, field = "Abstract.Note")
refDoc_manTags <- docvars(refCorp, field = "Manual.Tags")
refDoc_autoTags <- docvars(refCorp, field = "Automatic.Tags" )
refDoc_itemType <- docvars(refCorp, field = "Item.Type")
refDoc_pubTitle <- docvars(refCorp, field = "Publication.Title")
refDoc_pubYear <- docvars(refCorp, field = "Publication.Year")

```

  refDoc_title 
    refDoc_absNote
    refDoc_manTags
    refDoc_autoTags
    refDoc_itemType
    refDoc_pubTitle
    refDoc_pubYear

###   CODE: Docvar: absDoc Group
```{r Docvars: asbCorp Group , echo=TRUE}

absDoc_title <- docvars(absCorp, field = "Title")
absDoc_absNote<- docvars(absCorp, field = "Abstract.Note")
absDoc_manTags <- docvars(absCorp, field = "Manual.Tags")
absDoc_autoTags <- docvars(absCorp, field = "Automatic.Tags" )
absDoc_itemType <- docvars(refCorp, field = "Item.Type" )
absDoc_pubTitle <- docvars(absCorp, field = "Publication.Title")
absDoc_pubYear <- docvars(absCorp, field = "Publication.Year")
absDoc_libCat <- docvars(absCorp, field = "Library.Catalog")

```
    
  absDoc_title
    absDoc_absNote
    absDoc_manTags
    absDoc_autoTags
    absDoc_itemType
    absDoc_pubTitle
    absDoc_pubYear
    absDoc_libCat

#   CODE GROUP: CORPUS SUBSET
###       CODE: Corpus Subset: Signal   

Document Level Variables:
    Title 
    Manual.Tags
    
    Signal - Corpus Subset
```{r Corpus Subset: refCorp: Signal, include=FALSE}

s_tle_refCorpSub <- corpus_subset(refCorp, Title %in% 
  c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )

s_mTag_refCorpSub <- corpus_subset(refCorp, Manual.Tags %in%
   c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )                                  

```
      
  s_tle_refCorpSub
  s_mTag_refCorpSub
  
      
```{r Corpus Subset: absCorp: Signal, include=FALSE}

s_tle_absCorpSub <- corpus_subset(absCorp, Title %in% 
  c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )   

s_mTag__absCorpSub <- corpus_subset(absCorp, Manual.Tags %in%
  c("Dystopia", "Dystopias","Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
  "Utopia","Utopias", "Utopian","Utopianism")
  )   

```
  
  s_title_absCorpSub
  s_mTag__absCorpSub

###       CODE: Corpus Subset: Noise 

Document Level Variables:
    Title 
    Manual.Tags

```{r Corpus Subset: refCorp: Noise;, include=FALSE}

n_tle_refCorpSub <- corpus_subset(refCorp, Title %in% 
   c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)


n_mTag_refCorpSub <- corpus_subset(refCorp, Manual.Tags %in% 
  c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)


```
  
  n_tle_refCorpSub
  n_MTag_refCorpSub
  
```{r Corpus Subset: absCorp: Noise;, include=FALSE}

n_tle_absCorpSub <- corpus_subset(absCorp, Title %in% 
  c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)


n_mTag_absCorpSub <- corpus_subset(absCorp, Manual.Tags %in%
  c("apocalypse", "apocalyptic","post-apocalypse",
  "end of the world", "post apocalyptic",
  "Technology", "Society","Fiction", "Science Fiction",
  "Novel", "Literature")
)

```
  
  n_tle_absCorpSub
  n_mTag_absCorpSub

##       RETURNS: CORPUS SUBSET: Signal & Noise

    Signal 
      refCorpSub Group
  s_tle_refCorpSub
    returns: 11
  s_mTag_refCorpSub
    returns: 1

    Signal 
      absCorpSub Group
  s_tle_absCorpSub
    returns: 0
  s_mTag__absCorpSub
    returns: 0
    
    Noise
      refCorpSub Group
  n_tle_refCorpSub
    returns: 14
  n_MTag_refCorpSub
    returns: 1
    
    Noise
      absCorp Group
  n_tle_absCorpSub
    returns: 7
 n_mTag_absCorpSub
    returns: 0




#   CODE GROUP: Tokens
###    CODE: Tokens: Corpa
  
    absTok
    refTok
```{r Tokenize: AbsCorp & RefCorp eval=FALSE, include=FALSE}
# Tokenize 
absTok <- tokens(absCorp, remove_punct = TRUE)


refTok <- tokens(refCorp, remove_punct = TRUE)


```

###    CODE: Tokens: Docvars Categories
  
  Docvars Categories
      Title
      Abstract.Note
      Manual.Tags
      Automatic.Tags
      Item.Type
      Publication.Title
      Publication.Year //numbers cannot be tokenized//
      abscorp - Library.Catalog

      refTok Group 
```{r Tokenize: RefDoc Group, echo=TRUE}

title_refTok <- tokens(refDoc_Title)

absNote_refTok <- tokens(refDoc_AbsNote)

manTag_refTok <- tokens(refDoc_ManTags)

itmTyp_refTok <- tokens(refDoc_itemType)

pubTle_refTok <- tokens(refDoc_pubTitle)

```
    
  title_refTok
    absNote_refTok
    manTag_refTok
    itmTyp_refTok 
    pubTle_refTok 
    
    absTok Group
```{r Tokenize: absDoc Group, echo=TRUE}

title_absTok <- tokens(absDoc_Title)

absNote_absTok <- tokens(absDoc_AbsNote)

manTag_absTok <- tokens(absDoc_manTags)

itmTyp_absTok <- tokens(absDoc_itemType)

cent_absTok <- tokens(absDoc_Cent)
```
    
  title_absTok
    absNote_absTok
    manTag_absTok
    itmTyp_absTok
    cent_absTok
    
    
###    CODE: Token KWIC: Signal: Dyo Uto

        Titles
        Abstract Notes
        Manual Tags
      
    Signal refKwt Group
```{r Kwic: Signal: refTok Group}

     #Titles
sUto_tle_refKwt <- 
  kwic(title_refTok, pattern = 
         c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_tle_refKwt <- 
  kwic(title_refTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Abstract Note
sUto_aNote_refKwt <- 
  kwic(absNote_refTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)
  

sDyo_aNote_refKwt <- 
  kwic(absNote_refTok, pattern = 
         c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Manual Tags
sUto_mTags_refKwt <- 
  kwic(manTags_refTok,pattern = 
      c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)   

sDyo_mTags_refKwt <- 
  kwic(manTags_refTok,pattern = 
       c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

```
  
  Signal: Titles 
    sUto_tle_refKwt
    sDyo_tle_refKwt
  
  Signal: Abstract Note
    sUto_aNote_refKwt
    sDyo_aNote_refKwt
  
  Signal: Manual Tags
    sUto_mTags_refKwt
    sDyo_mTags_refKwt
     
    Signal: absKwt Group 
```{r Kwic: Signal: absTok Group}

    # Title
sUto_tle_absKwt <- 
  kwic(title_absTok, pattern = 
       c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_tle_absKwt <- 
  kwic(title_absTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Abstract Note
sUto_aNote_absKwt <- 
  kwic(absNote_absTok, pattern = 
        c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_aNote_absKwt <- 
  kwic(absNote_absTok, pattern = 
      c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

    # Manual Tags
sUto_mTags_absKwt <- 
  kwic(manTags_absTok,pattern = 
     c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

sDyo_mTags_absKwt <- 
  kwic(manTags_absTok,pattern = 
    c("Dystopia","Dystopias", "Dystopian","Dystopic","Anti-Utopian","AntiUtopian",
"Utopia","Utopias", "Utopian","Utopianism")
)

```

  Signal: Titles 
    sUto_tle_absKwt
    sDyo_tle_absKwt
  
  Signal: Abstract Note
    sUto_aNote_absKwt
    sDyo_aNote_absKwt
  
  Signal: Manual Tags
    sUto_mTags_absKwt
    sDyo_mTags_absKwt                   
          
###    CODE: Token KWIC: Signal: Wildcard: Uti* Dyi* 

  Signal Wildcard
      sUti = Utopi*
      sDyi = Dystopi*

  
    refKwt Wildcard Group
```{r Kwic: refTok Group: Signal: Wildcards, include=FALSE}

    # Titles 
sUti_tle_refKwt <- kwic(title_refTok,
          pattern = "utopi*", )

sDyi_tle_refKwt <- kwic(title_refTok,
          pattern = "dystopi*", )

    # Abstract Note
sUti_aNote_refKwt <- kwic(absNote_refTok,
          pattern = "utopi*", )

sDyi_aNote_refKwt <- kwic(absNote_refTok,
          pattern = "dystopi*",)

    # Manual Tags
sUti_mTags_refKwt <- kwic(manTags_refTok,
          pattern = "utopi*", )

sDyi_mTags_refKwt <- kwic(manTags_refTok,
          pattern = "dystopi*", )

```

  Signal: Wildcards: Titles
    sUti_tle_refKwt
    sDyi_tle_refKwt
    
  Signal: Wildcards: Abstract Note
    sUti_aNote_refKwt
    sDyi_aNote_refKwt
    
  Signal: Wildcards: Manual Tags
    sUti_mTags_refKwt
    sDyi_mTags_refKwt  


      absKwt Wildcard Group
```{r Kwic: Signal: absTok Group: Wildcard, eval=FALSE, include=FALSE}

# Titles 
sUti_tle_absKwt <- kwic(title_absTok,
          pattern = "utopi*", )

sDyi_tle_absKwt <- kwic(title_absTok,
          pattern = "dystopi*", )

    # Abstract Note
sUti_aNote_absKwt <- kwic(absNote_absTok,
          pattern = "utopi*", )

sDyi_aNote_absKwt <- kwic(absNote_absTok,
          pattern = "dystopi*",)

    # Manual Tags
sUti_mTags_absKwt <- kwic(manTags_absTok,
          pattern = "utopi*", )

sDyi_mTags_absKwt <- kwic(manTags_absTok,
          pattern = "dystopi*", )

```

  Signal: Wildcards: Titles
    sUti_tle_absKwt
    sDyi_tle_absKwt
    
  Signal: Wildcards: Abstract Note
    sUti_aNote_absKwt
    sDyi_aNote_absKwt
    
  Signal: Wildcards: Manual Tags
    sUti_mTags_absKwt
    sDyi_mTags_absKwt  


###    CODE: Token KWIC: Noise: A,T, D, S
    
    Noise: refKwt Group
```{r Kwic: Noise: refTok Group, eval=FALSE, include=FALSE}

          # Titles 
nApo_tle_refKwt <- kwic(title_refTok,
          pattern = c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
          )

nTop_tle_refKwt <- kwic(title_refTok,
          pattern = c("Technology", "Society","Fiction")
          )
 
nSub_tle_refKwt <- kwic(title_refTok,
          pattern = c("Novel", "Literature")
          )


          # Abstract Note
nApo_aNote_refKwt <- kwic(absNote_refTok ,
          pattern = c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
          )

nSub_aNote_refKwt  <- kwic(absNote_refTok ,
          pattern = c("Novel", "Literature")
          ) 
            

 nTop_aNote_refKwt <- kwic(absNote_refTok ,
          pattern = c("Technology", "Society","Fiction")
          )

          #Manual Tags
 nApo_mTag_refKwt <- kwic(manTags_refTok ,
          pattern = c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
          )

 nSub_mTag_refKwt  <- kwic(manTags_refTok ,
          pattern = c("Novel", "Literature")
          ) 
            

nTop_mTag_refKwt <- kwic(manTags_refTok ,
          pattern = c("Technology", "Society","Fiction")
          )

```

  Noise: Titles 
    nApo_tle_refKwt 
    nTop_tle_refKwt
    nSub_tle_refKwt

  Noise: Abstract Note
    nApo_aNote_refKwt
    nSub_aNote_refKwt
    nTop_aNote_refKwt
  
  Noise: Manual Tags
    nApo_mTag_refKwt
    nSub_mTag_refKwt
    nTop_mTag_refKwt
  
    Noise: absKwt Group  
```{r Kwic: Noise: absTok Group, eval=FALSE, include=FALSE}

# Titles 
nApo_tle_absKwt  <- 
  kwic( title_absTok, pattern = 
          c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
        )

nSub_tle_absKwt  <-
  kwic( title_absTok, pattern = 
          c("Novel", "Literature")
        ) 
            

nTop_tle_absKwt <- 
  kwic( title_absTok, pattern = 
          c("Technology", "Society","Fiction")
        )

# Abstract Note
nApo_aNote_absKwt <- 
  kwic( absNote_absTok, pattern = 
          c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
        )

nSub_aNote_absKwt  <- 
  kwic( absNote_absTok, pattern = 
          c("Novel", "Literature")
        ) 
            
nTopaNote_absKwt <- 
  kwic(absNote_absTok,
       pattern = 
         c("Technology", "Society","Fiction")
       )

#Manual Tags
nApo_mTag_absKwt <- 
  kwic( manTag_absTok, pattern = 
          c("post-apocalypse","apocalypse", "apocalyptic", "end of the world")
        )

nSub_mTag_absKwt  <- 
  kwic( manTag_absTok, pattern = 
          c("Novel", "Literature")
        ) 
            

nTop_mTag_absKwt<- 
  kwic( manTag_absTok, pattern = 
          c("Technology", "Society","Fiction")
        )

```

  Noise: Titles 
        nApo_tle_absKwt 
        nTop_tle_absKwt
        nSub_tle_absKwt

  Noise: Abstract Note
        nApo_aNote_absKwt
        nSub_aNote_absKwt
        nTop_aNote_refKwt
  
  Noise: Manual Tags
        nApo_mTag_absKwt
        nSub_mTag_absKwt
        nTop_mTag_absKwt






#   Basic Analysis: Topic Modeling
###       CODE: Label Topics
```{r CODE: Label Topics, echo=FALSE}
# Corpa
  tmTestCorp <- absDoc_absNote

# DFM
  tmT_dfm <- tokens(
    tmTestCorp,
      remove_punct = T,
      remove_symbols = T,
      remove_numbers = T,
    )%>%
    tokens_remove(
      stopwords("en"),
      min_nchar = 5
    )%>%
   dfm()

# Label Topics
    # K = Number of Topics
k = 5

 tmT_stm <- convert(
   tmT_dfm, to = "stm")

 tmT_stmOut <- stm(
  documents = tmT_stm$documents,
  vocab = tmT_stm$vocab,
  data = tmT_stm$meta,
  K = k,
  seed = 1234,
  init.type = "Spectral",
  verbose = FALSE
)
    # Show and print the topic labels,
labelTopics(tmT_stmOut)

    # the most frequent words in each topic
plot(tmT_stmOut, type = "summary")

```

###       CODE: Topic Names

```{r TEST CODE: Topic Names, echo=FALSE}
  tNameTest <- labelTopics(
    tmT_stmOut, 
    n = 5)$frex

# set up an empty vector
 tLabelTest <- rep(NA, k)

# set up a loop to go through the topics and collapse the words to a single name
for (i in 1:k) {
 tLabelTest[i] <- 
    paste(tNameTest[i,], collapse = "_")
}

# print the names
tNameTest

```
    Create the topic strings, 
using the `frex` parameter of the topic labels, 
choosing words that are the most `fr`equent *and* `ex`clusive in each 


##   Basic Analysis: Docvars Categories

    refGroup VS absGroup
###       CODE: Top Features: Titles

    refDfm Group 
    
```{r CODE: Top Feature: refDoc Group, echo=TRUE}
refTle_corp <- refTitles
  
refDfm_titles <- tokens(refTitles,
      remove_punct = T,
      remove_symbols = T) %>%
    tokens_remove(
      stopwords("en"), 
      min_nchar = 5)%>%
   dfm()

  topfeatures(refDfm_titles, 10)
```

```{r CODE: Top Feature: refDoc Group, echo=TRUE}

 refDoc_absNote_corp <-  corpus(refDoc_absNote)
   
   refDoc_absNote_dfm <- 
     tokens(refDoc_absNote_corp,
     remove_punct = T,
        remove_symbols = T) %>%
      tokens_remove(
        stopwords("en"), 
        min_nchar = 5)%>%
   dfm()

topfeatures( refDoc_absNote_dfm, 10)
```

```{r CODE: Top Feature: refDoc Group, echo=TRUE}

```

   



###       CODE: 





#   VISUALSATION: WordCloud 
##    Signal VS Noise: Titles
###   CODE: Kwic Title: Copra
    Turn Kwic Objects into Corpa
```{r CODE: CORPUS: Kwic: Titles, include=FALSE}
# TITLE
  
  # Utopia
    
    cRef_uti_Tle <- corpus(sUti_tle_refKwt)
    cRef_uto_Tle <- corpus(sUto_tle_refKwt)
    
    cAbs_uti_Tle <- corpus(sUti_tle_absKwt)
    cAbs_uto_Tle <- corpus(sUto_tle_absKwt)
  
  # Dystopia
    
    cRef_dyi_Tle <- corpus(sDyi_tle_refKwt)
    cRef_dyo_Tle <- corpus(sDyo_tle_refKwt)
    
    cAbs_dyi_Tle <- corpus(sDyi_tle_absKwt)
    cAbs_dyo_Tle <- corpus(sDyo_tle_absKwt )
    
  # Noise
    
    cRef_apo_Tle <- corpus(nApo_tle_refKwt)
    cRef_top_Tle <- corpus(nTop_tle_refKwt)
    cRef_sub_Tle <- corpus(nSub_tle_refKwt)
    
    cAbs_apo_Tle <- corpus(nApo_tle_absKwt)
    cAbs_top_Tle <- corpus(nTop_tle_absKwt)
    cAbs_sub_Tle <- corpus(nSub_tle_absKwt)
    
```


####   CODE: Kwic Title: Copra Combo: [refCorp + absCorp]      


```{r CODE: CORPUS: Title Combo [refCorp + absCorp], echo=FALSE}

# Title Corp [ref+abs]

        # Error [ref+abs] Utopi
    
        # 728 documents: [ref+abs] Subjects  
    sub_tleCom <-
      cAbs_sub_Tle +
      cRef_sub_Tle
    
        # 1464 documents: [ref+abs] Topics
    top_tleCom <- 
      cAbs_top_Tle + 
      cRef_top_Tle
    
    # 2574 documents: [ref+abs] Dystopi* 
    dyi_tleCom <-
      cRef_dyi_Tle +
      cAbs_dyi_Tle
    
      # 2896 documents: [ref+abs] Dystopi* + Apo Terms
    dyiApo_tleCom <-
      dyi_tleCom + apo_tleCom
    
    #  322 documents: [ref+abs] Apo Terms
    apo_tleCom  <- 
      cRef_apo_Tle +
      cAbs_apo_Tle
    
    #  1050 documents: [ref+abs] Apo Terms +  Subject
   apoSub_tleCom <-
      apo_tleCom +
      sub_tleCom  
   
    # Next Test
    
    testVar <-
    
     summary(testVar)

```

    Error  Utopia [ref+abs]
 
    sub_tleCom
728 documents: Subjects [ref+abs] 
    
    top_tleCom 
1464 documents: Topics [ref+abs]       

    dyi_tleCom
 2574 documents: Dystopi* [ref+abs] 
 
    dyiApo_tleCom
2896 documents: [ref+abs] Dystopi* + Apo Terms

    apoSub_tleCom
1050 documents: [ref+abs] Apo Terms +  Subject
  
    apo_tleCom 
322 documents: Apocryphal [ref+abs] 

####   CODE: Kwic Title: Copra Combo: [refCorp]      

```{r CODE: CORPUS: Title Combo [refCorp], echo=FALSE}

   # refCorp - Title Combo

         # 76 documents: [ref] Dystopi* + Utopi*
  ref_DyiUti_tleCom <-
    cRef_dyi_Tle + 
    cRef_uti_Tle  
   
       #  90 documents: [ref] Dystopi* + Utopi* + Apo Terms
  ref_apoUtiDyi_tleCom <-
      tle_DyiUti_refCorp +
      cRef_apo_Tle 
 

       # 32 documents: [ref] Dystopi* + Apo Terms
  ref_apoDyi_tleCom <-
      cRef_dyi_Tle + 
      cRef_apo_Tle

       # 72 documents: [ref] Utopi + Apo Terms
   ref_apoUti_tleCom <-
      cRef_uti_Tle +
      cRef_apo_Tle 
 
        # 80 documents: [ref] Utopi + Subject
   ref_subUti_tleCom <-
      cRef_uti_Tle + 
      cRef_sub_Tle  
      
        # 1522documents: [ref] Utopi + Topic
   ref_subTop_tleComp <-
      cRef_uti_Tle + 
      top_tleCom 

  
         # 36 documents: [ref] Apo Terms + Subject
    ref_apoSub_tleCom <-
      cRef_apo_Tle +
      cRef_sub_Tle
      
        # 340 documents: [ref] Dystopi* + Apo Terms
    refDyi_apoTleCom <-
        cRef_dyi_Tle + 
        apo_tleCom 

       #  398 documents: [ref] Dystopi* + Utopi* + [ref+abs] Apo Terms
  refDyiUti_apoTeCom <-
      tle_DyiUti_refCorp +
       apo_tleCom 
    
        #  380 documents: [ref] Utopi + [ref+abs] Apo Terms
   refUti_apoTleCom <-
        cRef_uti_Tle +
        apo_tleCom 
   
# Error: Cannot combine corpora with duplicated document names
#     For Documentation See defDysVarriables.Rmd 
    # WordCloud: Kwic Titles: Variables
    ### Kwic Titles: Error  
     
```


     ref_DyiUti_tleCom
76 documents: [ref] Dystopi* + Utopi*

    ref_apoUtiDyi_tleCom 
90 documents: [ref] Dystopi* + Utopi* + Apo Terms
    
    ref_apoDyi_tleCom
32 documents: [ref] Dystopi* + Apo Terms

        
    ref_apoUti_tleCom
72 documents: [ref] Utopi + Apo Terms
 
    ref_subUti_tleComp
80 documents: [ref] Utopi + Subject

     ref_subTop_tleComp
108 documents: [ref] Utopi + Topic

    ref_apoSub_tleCom
36 documents: [ref] Apo Terms + Subject
    
    refDyi_apoTleCom    
340 documents: [ref] Dystopi* + Apo Terms   
    
    refDyiUti_apoTeCom   
398 documents: [ref] Dystopi* + Utopi* + [ref+abs] Apo Terms

     refUti_apoTleCom
380 documents: [ref] Utopi + [ref+abs] Apo Terms


####   CODE: Kwic Title Copra: Combo: [absCorp]      

```{r CODE: CORPUS: Title Combo [absCorp], echo=FALSE}

# absCorp - Titles  


# Error: absCorp Dystopi* + Utopi*
  
        # 2104 documents: [abs] Utopi + [ref+abs] Apo Terms
    abs_apoUti_tleCom <- 
      cAbs_uti_Tle + 
      cAbs_apo_Tle
        
        # 2864  documents: [abs] Dystopi* + [ref+abs] Apo Terms
    abs_apoDyi_tleCom <-
      cAbs_dyi_Tle + 
      cAbs_apo_Tle


        # 1722 documents: [abs] Apo Terms + Topic
    abs_apoTop_tleCom <- 
      cAbs_apo_Tle + 
      cAbs_top_Tle 


        #  1014 documents: [abs] Apo Terms + Subject
    abs_apoSub_tleCom <- 
      cAbs_apo_Tle + 
      cAbs_sub_Tle 

        # 2118 documents: [abs] Utopi + [ref+abs] Apo Terms
    absUti_apoTleCom <-
        cAbs_uti_Tle + 
        apo_tleCom 
    
# Error: Cannot combine corpora with duplicated document names
#     For Documentation See defDysVarriables.Rmd 
    # WordCloud: Kwic Titles: Variables
    ### Kwic Titles: [absCorp] - Title Corp 
     

```
 
    Error: absCorp Dystopi* + Utopi*
  
    abs_apoUti_tleCom
2104 documents: [abs] Utopi + [ref+abs] Apo Terms
    
    abs_apoDyi_tleCom
2864  documents: [abs] Dystopi* + [ref+abs] Apo Terms


    abs_apoTop_tleCom 
1722 documents: [abs] Apo Terms + Topic

    abs_apoSub_tleCom 
1014 documents: [abs] Apo Terms + Subject  

    absUti_apoTleCom
2118 documents: [abs] Utopi + [ref+abs] Apo Terms    


### CODE: Word Cloud: Kwic Titles
### CODE: Word Cloud: Titles: refCorp + absCorp Combos
####   CODE: Word Cloud: Titles: [r+aCom] 2574 Doc: Dystopia Wildcard 

    WordCloud & TextStat Frequency
```{r CODE: DFM: Dys Wild Card Title, echo=FALSE}
# Tokenize & DTM
  
  dyi_tleDtm <- dyi_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm

```

```{r CODE: Wordcloud: Dys Wild Card: Title, echo=FALSE}
# Generate Word Cloud
  
textplot_wordcloud(dyi_tleDtm, max_words = 25)
textstat_frequency(dyi_tleDtm, 25)

textplot_wordcloud(dyi_tleDtm, max_words = 50)
textstat_frequency(dyi_tleDtm, 50)

textplot_wordcloud(dyi_tleDtm, max_words = 100)
textstat_frequency(dyi_tleDtm, 100)
```


####   CODE: Word Cloud: Titles: [r+aCom]  728 Doc: Subjects 
``` {r CODE: DFM: , echo=FALSE}
# Tokenize & DTM
# 728 documents: Subjects [ref+abs] 

  sub_tleComDtm <-  sub_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = F) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm

# Generate Word Cloud

textplot_wordcloud(sub_tleComDtm, max_words = 100)

textstat_frequency(sub_tleComDtm, 100)

```

####   CODE: Word Cloud: Titles: [r+aCom] 1464 Doc: Topics  
``` {r CODE: DFM: , echo=FALSE}
# Tokenize & DTM
# 1464 documents: Topics [ref+abs] 

  top_tleComDtm <-  top_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 3) %>%                                     
    tokens_wordstem %>%
    dfm
# Generate Word Cloud
# 

textplot_wordcloud(top_tleComDtm, max_words = 100)

textstat_frequency(top_tleComDtm, 100)
```

####   CODE: Word Cloud: Titles: [r+aCom]  322 Doc: Apocryphal  
``` {r CODE: DFM: , echo=FALSE}
# Tokenize & DTM
# 322 documents: Apocryphal [ref+abs]

 apo_tleComDtm <- apo_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm
```

``` {r CODE: Wordcloud: , echo=FALSE}

# Generate Word Cloud
# 322 documents: Apocryphal [ref+abs]

textplot_wordcloud(apo_tleComDtm, max_words = 100)

textstat_frequency(apo_tleComDtm, 100)

```


####   CODE: Word Cloud: Titles: [r+aCom] 2588 Doc: Dystopi* + Apo Terms
```{r CODE: DFM: Titles: Dystopi Apo Terms, echo=FALSE}
# Tokenize & DTM
# 2588 documents: Dystopi* + Apo Terms
  
  dyiApo_tleDtm <- dyiApo_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm

# Generate Word Cloud
  
textplot_wordcloud(dyiApo_tleDtm, max_words = 25)
textstat_frequency(dyiApo_tleDtm, 25)

textplot_wordcloud(dyiApo_tleDtm, max_words = 50)
textstat_frequency(dyiApo_tleDtm, 50)

textplot_wordcloud(dyiApo_tleDtm, max_words = 100)
textstat_frequency(dyiApo_tleDtm, 100)


```






    NOTES:
  Unable to combine Utopia titles for refCorp & absCorp

### CODE: Word Cloud: Titles: refCorp 
####   CODE: Word Cloud: Titles: [refCorp]   58 doc: Utopi*
58 Documents
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 58 Documents

  cRef_uti_TleDtm <- cRef_uti_Tle %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm

# Generate Word Cloud

textplot_wordcloud(cRef_uti_TleDtm, max_words = 25)

textstat_frequency(cRef_uti_TleDtm, 25)

```

####   CODE: Word Cloud: Titles: [refCorp] 1522 doc: Utopi + [r+aCom] Topic 

1522 documents 

``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 1522documents: [ref] Utopi + [ref+abs] Topic

  ref_subTop_tleCompDtm <-  ref_subTop_tleComp%>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm


# Generate Word Cloud

textplot_wordcloud(ref_subTop_tleCompDtm, max_words = 100)

textstat_frequency(ref_subTop_tleCompDtm, 100)

```









####   CODE: Word Cloud: Titles: [refCorp] 76 doc: Dystopi* + Utopi*
 76 documents
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 76 documents: [ref] Dystopi* + Utopi*

   ref_DyiUti_tleComDtm <-  ref_DyiUti_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm


# Generate Word Cloud

textplot_wordcloud(ref_DyiUti_tleComDtm , max_words = 20)

textstat_frequency(ref_DyiUti_tleComDtm , 20)

```


####   CODE: Word Cloud: Titles: [refCorp] 398 doc: Dystopi* + Utopi* + [r+aCom] Apo Terms
398 documents: [refCorp] Dystopi* +  Utopi* + [r+aCom]  Apo Terms
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 398 documents: [refCorp] Dystopi* + Utopi* + [r+aCom] Apo Terms

  refDyiUti_apoTeComDtm <- refDyiUti_apoTeCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm

# Generate Word Cloud

textplot_wordcloud(refDyiUti_apoTeComDtm, max_words = 100)

textstat_frequency(refDyiUti_apoTeComDtm, 100)

```

### CODE: Word Cloud: Titles: absCorp 
        
        Error [absCorp] doc: Dystopi* + Utopi*
        Error [absCorp] Utopi +  [r+aCom] Topic


####   CODE:Word Cloud: Titles:   58 doc: [absCorp]  Utopi*
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
#  58 docs

 cRef_uti_TleDtm <-  cRef_uti_Tle %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm

dim(cRef_uti_TleDtm)


# Generate Word Cloud

textplot_wordcloud(cRef_uti_TleDtm, max_words = 50)

textstat_frequency(cRef_uti_TleDtm, 50)

```



####   CODE:Word Cloud: Titles:   18 doc: [absCorp] Dystopi* 
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 

  cRef_dyi_TleDtm <-  cRef_dyi_Tle %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm

dim(cRef_dyi_TleDtm)

# Cannot Generate Word Cloud

```



####   CODE:Word Cloud: Titles: 2864 doc: [absCorp] Dystopi* + Utopi* + [r+aCom] Apo Terms
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 

  abs_apoDyi_tleComDtm <-  abs_apoDyi_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm


# Generate Word Cloud

textplot_wordcloud(abs_apoDyi_tleComDtm , max_words = 100)

textstat_frequency(abs_apoDyi_tleComDtm , 100)

```



####   CODE:Word Cloud: Titles: 2104 doc: [absCorp] Utopi + [r+aCom] Apo 
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 

  abs_apoUti_tleComDtm <-  abs_apoUti_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm


# Generate Word Cloud

textplot_wordcloud(abs_apoUti_tleComDtm, max_words = 100)

textstat_frequency(abs_apoUti_tleComDtm, 100)

```



####   CODE:Word Cloud: Titles: 1722 doc: [absCorp] Apo Terms + Topic
``` {r CODE: WordCloud: , echo=FALSE}
# Tokenize & DTM
# 1722 documents: [abs] Apo Terms + Topic

  abs_apoTop_tleComDtm <- abs_apoTop_tleCom %>%
    tokens(
      remove_punct = T, 
      remove_numbers = T, 
      remove_symbols = T) %>%   
    tokens_tolower %>%                                                    
    tokens_remove(stopwords('en'),
      min_nchar = 5) %>%                                     
    tokens_wordstem %>%
    dfm


# Generate Word Cloud

textplot_wordcloud(abs_apoTop_tleComDtm, max_words = 100)

textstat_frequency(abs_apoTop_tleComDtm, 100)

```


##
# TBD Word Cloud - Generate Varriables
## TBD: Signal VS Noise: Abstract
## TBD: Signal VS Noise: Manual Tags
## TBD: Signal VS Noise: ** Item Type**

# On Deck: Dictionary Search